### 2022-07-24 latex/Chapters/DRLSearch.tex
update

@@

blabla

@@

see \cite{Watkins1992}

>>>>

TBD this is a bit of a verbiage chapter, where I go through the different techniques I have used and implemented for this project and give some references.

@@

see \cite{Sutton1998}

@@

see \cite{Watkins1992} and \cite{https://doi.org/10.48550/arxiv.1805.07470}

%----------------------------------------------------------------------------------------
%	SECTION 6
%----------------------------------------------------------------------------------------

\section{Monte Carlo Tree Search}

see \cite{https://doi.org/10.48550/arxiv.1805.07470} and \cite{AlphaGo}

### 2022-07-24 latex/Chapters/Examples.tex
update

In this chapter, I will go through some examples, illustrating how to use the code base to learn and solve various puzzles. For each section, simple examples of code will be indicated in air force blue \afblue \textbf{python code} \black paragraphs, and can easily be run from command line or copied into a script and run from your favourite IDE.

@@

%-----------------------------------
%	SUBSECTION 1.2
%-----------------------------------
\subsection{Deep Learner}
\label{DLSS}
blabla

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.39]{./Figures/examplenaivesolver}
%\decoRule
\caption[Examples]{naive solver}
\label{fig:examplenaivesolver}
\end{figure}

%-----------------------------------
%	SUBSECTION 2.3
%-----------------------------------
\subsection{Kociemba}
TBD

>>>>

In this chapter, I will go through some examples, illustrating how to use the code base to learn and solve various puzzles. For each section, simple examples of code will be indicated in \afblue \textbf{python code} \black paragraphs, and can easily be run from command line or copied into a script and run from your favourite IDE.

@@

The perfect learner has been discussed in details in \ref{sec:codelearners}. We simply show here how to run it to learn the value function for the (n=2, m=3) SP, that is, to solve all 360 possible configurations via an optimal solver (A{*} with Manhattan heuristic).

\afblue
\paragraph{}{\textbf{python code -- perfect learner}}
\begin{python}
####################################################################
from rubiks.heuristics.heuristic import Heuristic
from rubiks.puzzle.puzzle import Puzzle
from rubiks.learners.learner import Learner
from rubiks.utils.utils import get_model_file_name
####################################################################
action_type=Learner.do_learn
n=2
m=3
puzzle_type=Puzzle.sliding_puzzle
learner_type=Learner.perfect_learner
heuristic_type=Heuristic.manhattan
nb_cpus=4
learning_file_name=get_model_file_name(puzzle_type=puzzle_type,
                                       dimension=(n, m),
                                       model_name=Learner.perfect)
if __name__ == '__main__':
    # we fully solve the 2 x 3 SP ... should take ~5s
    Learner.factory(**globals()).action()
####################################################################
action_type=Learner.do_plot
if __name__ == '__main__':
    # we display the results
    Learner.factory(**globals()).action()
####################################################################
\end{python}
\black
The above snipet of code will solve the 2 by 3 SP and then display the results, showing the distribution of optimal costs, as well as the most difficult puzzle.

\begin{figure}[H]
\centering
\includegraphics[scale=0.45]{./Figures/exampleperfectlearner}
%\decoRule
\caption[Examples]{perfect learner example}
\label{fig:exampleperfectlearner}
\end{figure}

%-----------------------------------
%	SUBSECTION 1.2
%-----------------------------------
\subsection{Deep Learner}
\label{DLSS}
The DeepLearner, also discussed in details in \ref{sec:codelearners}, needs some training data. It could in principle of course be trained on any data, not necessarily optimal data (i.e. generated by an optimal solver). Here however, I make use of the TrainingData class to generate 100 sequences of fully solved (n=5, m=2) SP via A{*} with Manhattan++.

\afblue
\paragraph{}{\textbf{python code -- deep learner}}
\begin{python}
####################################################################
from math import inf
####################################################################
from rubiks.deeplearning.deeplearning import DeepLearning
from rubiks.learners.learner import Learner
from rubiks.learners.deeplearner import DeepLearner
from rubiks.puzzle.puzzle import Puzzle
from rubiks.puzzle.trainingdata import TrainingData
####################################################################
if '__main__' == __name__:
    puzzle_type = Puzzle.sliding_puzzle
    n = 5
    m = 2
    """ Generate training data - 100 sequences of fully 
    solved perfectly shuffled puzzles. 
    """
    nb_cpus = 4
    time_out = 600
    nb_shuffles = inf
    nb_sequences = 100
    TrainingData(**globals()).generate(**globals())
    """ DL learner """
    action_type = Learner.do_learn
    learner_type = Learner.deep_learner
    nb_epochs = 1000
    learning_rate = 1e-3
    scheduler = DeepLearner.gamma_scheduler
    gamma_scheduler = 0.9999
    save_at_each_epoch = False
    threshold = 0.01
    training_data_freq = 100
    high_target = nb_shuffles + 1
    training_data_from_data_base = True
    nb_shuffles_min = 20
    nb_shuffles_max = 50
    """ ... and its network config """
    network_type = DeepLearning.fully_connected_net
    layers_description = (100, 50, 10)
    one_hot_encoding = True
    """ Kick-off the Deep Learner """
    learning_file_name = Learner.factory(**globals()).get_model_name()
    Learner.factory(**globals()).action()
    """ Plot its learning """
    action_type = Learner.do_plot
    Learner.factory(**globals()).action()
####################################################################
\end{python}
\black

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.39]{./Figures/examplenaivesolver}
%\decoRule
\caption[Examples]{naive solver example}
\label{fig:examplenaivesolver}
\end{figure}

%-----------------------------------
%	SUBSECTION 2.3
%-----------------------------------
\subsection{Kociemba}
TBI \& TBD
